|

### 2021-10-06 03-Chp-Systematic-Review.Rmd
Back to working versions

Following best practice, where summary data was presented across two groups (e.g. age at baseline stratified by hypercholesterolemia status), the following approach was used to combine the groups:[@higgins2019]

@@

This additional appraisal marks a departure from the registered protocol, as there was initially no intention to try and examine the risk of bias due to missing evidence. This is largely because the tool did not exist when the protocol was originally registered.

@@

_[Note: Julian, I am particularly interested in your feedback on this section, and the corresponding results section (Section \@ref(sys-rev-including-preprints)), as I am not convinced on the language I am using]_

@@

The database search identified `r num_to_text(23447)` records, of which `r comma(7338)` were duplicated records. Of the random sample of 500 records screened to ensure the accuracy of the study design filters, no eligible records were identified. Many of those excluded by the filters were basic science studies, commentaries or educational articles, as expected. <!-- TODO include some example citations here -->

@@

The majority of included studies described non-randomised analyses, with the sole two included randomised controlled trials (the Heart Protection Study/British Heart Foundation trial[@heartprotectionstudycollaborativegroup2002] and the JUPITER trial[@ridker2008]) both reporting on the effect of statin use on all-cause dementia in older adults. A similarly small number of Mendelian randomisation studies were identified, several of which employed a two-sample approach using the identical summary statistics from published genome wide association studies (GWAS) leading to complications in the synthesis (see Section \@ref(sys-rev-res-AD)).

@@

In terms of outcomes, the vast majority of studies examined either all-cause dementia (`r n_Dementia`) or Alzheimer's disease (`r n_AD`), with only a small proportion examining vascular dementia `r n_VaD`. Some rarer outcome classifications such as vascular-component or mixed dementia were also investigated, but were myc rarer.

@@

Three included reports were preprints (denoted in the Table \@ref(tab:studyCharacteristics-table) using an asterisk),[@ridker2008; @so2017;@zhu2017] one of which had subsequently been published and was captured by the primary literature search.[@zhu2018] All three included preprints were obtained from the bioRxiv preprint server and all described a Mendelian randomisation analysis.

@@

Finally, there were several identified Mendelian randomisation studies examining the effect of genetically lowered LDL-c on Alzheimer's disease risk (Figure \ref(fig:mrDuplication)). However, all of these studies used a two-sample approach, making use of summary statistics from the GLGC and IGAP consortia. Due to this overlap, which would result in a falsely precise estimate caused by multiple counting of the same participants, no meta-analysis of these studies was performed. However, across all analysis, using varying number of SNPS, no evidence for an effect was observed (Figure \ref(mrDuplication)).

<!----------------------------------------------------------------------------->
(ref:mrDuplication-cap) Summary of duplication of Mendelian randomisation studies which used summary statistics from the Global Lipid Genetics Consortium (GLGC) and the International Genomics of Alzheimer's Project (IGAP). Note that the Alzheimer’s Disease Genetics Consortium (ADGC) is a sub-cohort within IGAP.

@@

```{r mrDuplication, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrDuplication-cap)', out.width='100%', fig.scap='(ref:mrDuplication-scap)'}
knitr::include_graphics(file.path("figures","sys-rev","mrDuplication.png"))
```
<!----------------------------------------------------------------------------->

>>>>

In line with best practice, where summary data was presented across two groups (e.g. age at baseline stratified by hypercholesterolemia status), the following approach was used to combine the groups:[@higgins2019]

@@

This additional appraisal marks a departure from the registered protocol, as there was initially no intention to try and examine the risk of bias due to missing evidence. This is largely because the tool did not exist when the protocol was registered.

@@

_[Note: Julian, I am particularly interested in your feedback on this section, and the corresponding results section (Section \@ref(sys-rev-including-preprints-res)), as I am not convinced on the language I am using]_

@@

The database search identified `r num_to_text(23447)` records, of which `r comma(7338)` were duplicated records. Of the random sample of 500 records screened to ensure the accuracy of the study design filters, no eligible records were identified. Many of those excluded by the filters were commentaries/educational articles, or described basic science studies. <!-- TODO include some example citations here -->

@@

The majority of included studies described non-randomised analyses, with the sole two included randomised controlled trials (the Heart Protection Study/British Heart Foundation trial[@heartprotectionstudycollaborativegroup2002] and the JUPITER trial[@ridker2008]) both reporting on the effect of statin use on all-cause dementia in older adults. A similarly small number of Mendelian randomisation studies were identified, several of which employed a two-sample approach using summary statistics from the same published genome wide association studies (GWAS) leading to complications in the synthesis (see Section \@ref(sys-rev-res-AD)).

@@

In terms of outcomes, the vast majority of studies examined either all-cause dementia (`r n_Dementia`) or Alzheimer's disease (`r n_AD`), with only a small proportion examining vascular dementia (`r n_VaD`). Some other outcome classifications such as vascular-component or mixed dementia were also investigated, but were much rarer.

@@

Three included reports were preprinted (denoted in the Table \@ref(tab:studyCharacteristics-table) using an asterisk),[@ridker2008; @so2017;@zhu2017] one of which had subsequently been published and was captured by the primary literature search.[@zhu2018] All three included preprints were obtained from the bioRxiv preprint server and all described a Mendelian randomisation analysis.

@@

Finally, there were several identified Mendelian randomisation studies examining the effect of genetically lowered LDL-c on Alzheimer's disease risk (Figure \@ref(fig:mrDuplication)). However, all of these studies used a two-sample approach, making use of summary statistics from the GLGC and IGAP consortia. Due to this overlap, which would result in a falsely precise estimate caused by multiple counting of the same participants, no meta-analysis of these studies was performed. However, across all analysis, using varying number of SNPS, no evidence for an effect was observed (Figure \@ref(fig:mrDuplication)).

<!----------------------------------------------------------------------------->
(ref:mrDuplication-cap) Summary of duplication across Mendelian randomisation studies which used summary statistics from the Global Lipid Genetics Consortium (GLGC) and the International Genomics of Alzheimer's Project (IGAP). Note that the Alzheimer’s Disease Genetics Consortium (ADGC) is a sub-cohort within IGAP.

@@

```{r mrDuplication, echo = FALSE, results="asis", fig.pos = "H", fig.align='center', fig.cap='(ref:mrDuplication-cap)', out.width='80%', fig.scap='(ref:mrDuplication-scap)'}
knitr::include_graphics(file.path("figures","sys-rev","mrDuplication.png"))
```
<!----------------------------------------------------------------------------->
